\documentclass[oneside]{article}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage{listings}
\usepackage[margin=0.75in]{geometry}
\usepackage{amsmath,amssymb,amsfonts}

\makeatletter

% Redefine author.
\def\author#1{\gdef\@author{#1}}
\def\@author{\@latex@warning@no@line{No \noexpand\author given}}
% Redefine title.
\def\email#1{\gdef\@email{#1}}
\def\@email{\@latex@warning@no@line{No \noexpand\email given}}
% Redefine organization.
\def\organization#1{\gdef\@organization{#1}}
\def\@organization{\@latex@warning@no@line{No \noexpand\organization given}}
% "libraryname" and "libraryversion".
\def\libraryname#1{\gdef\@libraryname{#1}}
\def\@libraryname{\@latex@warning@no@line{No \noexpand\libraryname given}}
\def\libraryversion#1{\gdef\@libraryversion{#1}}
\def\@libraryversion{\@latex@warning@no@line{No \noexpand\libraryversion given}}

\def\maketitle{%
\noindent\makebox[\textwidth]{%
	\uppercase{{\@organization} {\@libraryname} {\@libraryversion}}%
	\hfill
	\uppercase{{\@author} {(\href{\@email}{\@email})}}%
}%
}

\makeatother

\organization{Primordial Machine's}
\libraryname{Byte Order Library}
\libraryversion{v1.0}
\author{Michael Heilmann}
\email{michaelheilmann@primordialmachine.com}
\begin{document}
\lstset{language=C++,
  basicstyle=\footnotesize, % reduce the font size.
  showstringspaces=false    % do not display "squat-u" for whitespace.
}
\maketitle
\section{Synopsis}
C++ 17 library providing Byte order detection. 
The library is made available publicly on 
\href{https://github.com/primordialmachine/byte-order}{Github}
under the
\href{https://github.com/primordialmachine/byte-order/blob/master/LICENSE}{MIT License}.

\section{Limitations and Restrictions}
The library officially only supports Visual Studio 2017 and Windows 10.
The Byte Order for Windows 10 is always Little Endian.

\section{Introductory example}
To determine target environment's Byte order, evaluate the constant expression function \lstinline{get_byte_order}`
which returns an enum class element from the \lstinline{byte_order} enum class.

\begin{lstlisting}
#include "primordialmachine/byte_order/include.hpp"
#include <stdlib.h>

int main(int argc, char **argv) {
  using namespace primordialmachine;
  using namespace std;
  switch (get_byte_order()) {
    case byte_order::little_endian:
      {
        cout << "Environment Byte order is Little Endian"
             << std::endl; 
        return EXIT_SUCCESS;
      } break;
    case byte_order::big_endian:
      {
        cout << "Environment Byte order is Big Endian"
             << std::endl;
        return EXIT_SUCCESS;
      } break;
    default:
     {
        // This code should never be reached.
        err << "unable to determine Environment Byte order"
            << std::endl;
        return EXIT_FAILURE;
     }
  };
}
\end{lstlisting}
If the Byte order can not be determined, a compile-time error is raised i.e. the program will not compile.

\section{Building under Visual Studio 2017}
\begin{enumerate}
\item Open the solution \verb+byte-order.sln+ in Microsoft Visual Studio 2017.
\item Batch build everything.
\item The folder \verb+packages+ contains the distribution of the library i.e. include files and the
      static libraries for
  \begin{enumerate}
    \item the platforms \verb+Win32+ and \verb+x64+ and
    \item configurations \verb+Release+ and \verb+Debug+.
  \end{enumerate}
\item Copy the contents of the `packages` folder into a directory. Let
      \verb+[library home]+ be a placeholder denoting the path by which that folder
      can be referenced from your project. 
\item Add
  \begin{enumerate}
    \item the include path
\begin{verbatim}
[library home]/primordialmachine/byte-order/
$(Platform.toLower())/$(Configuration.toLower())/includes
\end{verbatim}
	and
    \item the library path
\begin{verbatim}
[library home]/primordialmachine/byte-order/
$(Platform.toLower())/$(Configuration.toLower())/libraries
\end{verbatim}
    to your project.
\end{enumerate}
\item Link your project with the library \verb+byte-order.lib+.
\item Add the include directive \lstinline{#include "primordialmachine/byte_order/include.hpp"} where appropriate.
\item You can now use the functionality provided by the library.
\end{enumerate}

\section{Library Interface Documentation}
\subsection{namespace primordialmachine}
The namespace this library is adding its declarations/definitions to.
The added namespace elements are documented below.
\subsection{enum class byte\_order}
An enum class of the Byte orders known to this library.
The contained enum class elements are documented below.
\begin{enumerate}
\item \lstinline{little_endian} enum class element denoting Little Endian Byte order.
\item \lstinline{big_endian} enum class element denoting Big Endian Byte order.
\end{enumerate}

\subsection{byte\_order get\_byte\_order()}
A parameterless constant expression function getting the target environment's Byte order. It returns
a value of type \lstinline{byte_order} denoting the target environment's Byte order.     If the Byte
order can not be determined, a compile-time error is raised i.e. the program will not       compile.
\end{document}
